---
title: "World cup success index (WCS_I) Visuals"
author: "Santiago Florimonte"
output:
  html_document:
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float:
      smooth_scroll: yes
      collapsed: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning=FALSE)
```

```{css}
  #TOC {
    max-width: 200px;
    }
  
```

```{r libraries set-up, include=FALSE}

library(DT) # datatable()
library(tidyverse)
library(png) # readPNG() 
library(dplyr) # anti_join(), inner_join(), left_join(), bind_cols()
library(grid) # rasterGrob()
library(rvest) # read_html(), html_nodes(), html_text(), html_attr()
library(stringr) # str_detect() 
library(reactable) # reactable()
library(ggplot2)
library(openxlsx) # read.xlsx(), write.xlsx()
library(sf) # st_as_sf() ; st_transform() ; st_geometry()
library(rnaturalearth) # ne_countries()  
library(rnaturalearthdata)
library(plotly) # plot_geo()
library(magick) # image_trim(), image_read(), image_scale() 
library(cowplot) #draw_image()
# HTML htmltools
# aggregate() stats
# as.raster() grDevices 


```

```{r initial datasets, eval=FALSE}

wc_22 <- lapply(list(wc_links_gs[1], wc_links_r16[1], wc_links_winners[1]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename( wc_countries = '.') %>%  count(wc_countries) 

wc_18 <- lapply(list(wc_links_gs[2], wc_links_r16[2], wc_links_winners[2]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename( wc_countries = '.') %>%  count(wc_countries) 

wc_14 <- lapply(list(wc_links_gs[3], wc_links_r16[3], wc_links_winners[3]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename( wc_countries = '.') %>%  count(wc_countries) 

wc_10 <- lapply(list(wc_links_gs[4], wc_links_r16[4], wc_links_winners[4]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename( wc_countries = '.') %>%  count(wc_countries) 

wc_06 <- lapply(list(wc_links_gs[5], wc_links_r16[5], wc_links_winners[5]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename( wc_countries = '.') %>%  count(wc_countries) 

wc_02 <- lapply(list(wc_links_gs[6], wc_links_r16[6], wc_links_winners[6]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename(wc_countries = '.') %>%  count(wc_countries) 

wc_98 <- lapply(list(wc_links_gs[7], wc_links_r16[7], wc_links_winners[7]), function(i){
  rbindlist(i)
}) %>% rbindlist() %>% rename(wc_countries = '.') %>%  count(wc_countries) 

# wc_98 -------

s_points <- numeric(0) 

for (i in wc_98$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_98 <- cbind(wc_98, s_points, label = rep("wc_98", 32))

# wc_02 -------

s_points <- numeric(0) 

for (i in wc_02$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_02 <- cbind(wc_02, s_points, label = rep("wc_02", 32))

# wc_06 -------

s_points <- numeric(0) 

for (i in wc_06$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_06 <- cbind(wc_06, s_points, label = rep("wc_06", 32))

# wc_10 -------

s_points <- numeric(0) 

for (i in wc_10$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_10 <- cbind(wc_10, s_points, label = rep("wc_10", 32))

# wc_14 -------

s_points <- numeric(0) 

for (i in wc_14$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_14 <- cbind(wc_14, s_points, label = rep("wc_14", 32))

# wc_18 -------

s_points <- numeric(0) 

for (i in wc_18$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_18 <- cbind(wc_18, s_points, label = rep("wc_18", 32))

# wc_22 -------

s_points <- numeric(0) 

for (i in wc_22$n) {
  if (i == 1 ) {
  s_points <- c(s_points, 0.2)
} else if (i == 2) {
  s_points <- c(s_points, 0.36)
} else if (i == 3) {
  s_points <- c(s_points, 0.52)
} else if (i == 4) {
  s_points <- c(s_points, 0.68)
} else if (i == 5) {
  s_points <- c(s_points, 0.84)
} else if (i == 6) {
  s_points <- c(s_points, 1)
}
  }

wc_22 <- cbind(wc_22, s_points, label = rep("wc_22", 32))


wc_all_s_points <- rbind(wc_98, wc_02, wc_06, wc_10, wc_14, wc_18, wc_22) %>% select(.,  - c('n', 'label')) %>% group_by(wc_countries) %>% summarise('sum_s_points' = sum(s_points)) %>% arrange(desc(sum_s_points))

wc_all_labeled_long <- rbind(wc_98, wc_02, wc_06, wc_10, wc_14, wc_18, wc_22)

wc_all_labeled_wide <- spread(wc_all_labeled, key = label, value = s_points) %>%
  replace_na(list(wc_98 = 0, wc_02 = 0, wc_06 = 0, wc_10 = 0, wc_14 = 0, wc_18 = 0, wc_22 = 0))

wc_all_labeled_wide_sum <- aggregate(wc_all_labeled.1[,2:9], 
          by = list(wc_countries = wc_all_labeled.1$wc_countries), FUN = sum)


  # Import to spreadsheets, just in case... Thanks Lorenzo.

# path_xlsx.s <- "C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_football//wc_success"
# 
# list_datasets <- list(wc_all_s_points, wc_all_labeled_long, wc_all_labeled_wide, 
#                       wc_all_labeled_wide_sum)
# 
# lapply(list_datasets, function(o){
#   write.xlsx(o, path_xlsx.s)  
# })

```

## **Summary**


 * **Context**
    * This project belongs to **Santiago Florimonte's portfolio**, and is part of **saint_analytics**, a business idea in the making.
 * **What you'll find**
    * Visuals around a success index for the most popular sports competition of all: The FIFA world cup
    * Tables containing datasets for the visuals, sources, and credits


```{r initial datasets from desktop}

wc_all_s_points <- read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//wc_all_s_points.xlsx")

wc_all_labeled_long <- read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//wc_all_labeled_long.xlsx")

wc_all_labeled_wide <- read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//wc_all_labeled_wide.xlsx")

wc_all_labeled_wide_sum <- read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//wc_all_labeled_wide_sum.xlsx")

```

```{r index n image dataset}
arg_expl_summ_df <- data.frame(summ = c("~ Argentina qualified\n~ 0.2", 
                                    "~ Came on top of group C\n~ 0.2 + 0.16 = 0.36", 
                                    "~ Won against Australia\n~ 0.36 + 0.16 = 0.52",
                                      "~ Dramatic win in penalty\nshotout vs Holland\n~ 0.52 + 0.16 = 0.68",
                                    "~ Comfortable win\nagainst Croatia.\n~ 0.68 + 0.16 = 0.84",
                                    "~ The 'Scaloneta' wins\nthe craziest WC final\n~ 0.84 + 0.16 = 1"), 
     x_coord = c(0.5, 1.5, 2.5, 
                 3.5, 4.5, 5.5), 
     y_coord = c(0.3, 0.46, 0.62,
                 0.78, 0.94, 1.1))

s_points_ip <- c(0.2, 0.36, 0.52, 0.68, 0.84, 1)
achieved_stage_ip <- c("Qualified", "Last 16", "Quarter finals", "Semi finals", "Final", "CHAMPS!!")
achieved_stage_ip <- factor(achieved_stage_ip, levels = c("Qualified", "Last 16", "Quarter finals", "Semi finals", "Final", "CHAMPS!!"))

ip_df <- data.frame(s_points_ip, achieved_stage_ip)

path_wc_0 <- "C://Users//santi//Desktop//wc_success_cup.png"
img_wc_0 <- image_read(path = path_wc_0) %>% image_scale(., "x400") 

img_wc_1 <- img_wc_0 %>% image_trim()

img_cred <- data.frame(
  imagery_tag = c("World Cup"),
  imagery_credit = c("Toppng.com"),
  imagery_link = c("https://toppng.com/free-image/trophy-world-cup-PNG-free-PNG-Images_8447"))

path_saint_1 <- "C://Users//santi//Desktop//saint_analytics//logo(s)//saint_analytics(11).png"

img_saint_01 <- image_read(path = path_saint_1) %>% image_scale(., "x500")

img_saint_1 <- img_saint_01 %>% image_trim()

pen <- readPNG("C://Users//santi//Desktop//saint_analytics//logo(s)//saint_analytics(11.bis).png") %>% as.raster()

```

## **Visuals**

### **WCS_I example**
```{r index visual, fig.align='center', fig.height=7, fig.width=11}

ggplot(ip_df, aes(x = achieved_stage_ip, y = s_points_ip)) +
  geom_col(fill = "#3399CC", alpha = 0.6) +
  scale_y_continuous(limits = c(-0.04,1.3), breaks = s_points_ip) +
  labs(title = "How WCS_I works", 
       subtitle = "WCS_I applied to current world champions: Argentina (a.k.a 'La Scaloneta')",
       x = '',
       y = "WCS_I") + 
  theme(plot.title = element_text(size = 18, face = 'bold', hjust = 0), 
        plot.subtitle = element_text(size = 14, face = 'bold', hjust = 0),
        axis.text = element_text(size = 14), axis.ticks.y = element_blank(), 
        panel.grid.major.y = element_line(color = 'gray', linewidth = .25, 
                                          linetype = "dashed"), 
        panel.background = element_blank()) +
  geom_segment(data = data.frame(x = 1, xend = 5.8, y = -.04, yend = -.04), 
               aes(x = x, xend = xend, y = y, yend = yend), 
           color = "#3399CC", alpha = 0.85,
           linewidth = 4, linejoin = c('mitre'),
           arrow = arrow(angle = 10, length = unit(0.4,'inches'))) +
  draw_image(img_wc_1, x = 5.5, y = 1, height = .25, scale = 1) +
  geom_label(data = arg_expl_summ_df[1,], 
             aes(x = 1, 
                 y = y_coord -0.18,  label = summ), 
             fill = "#3399CC", alpha = 0.1, size = 3) + 
  geom_label(data = arg_expl_summ_df[-1,], 
             aes(x = c(1,2,3,4,5), 
                 y = y_coord -0.18,  label = summ), 
             fill = "#3399CC", alpha = 0.6, size = 3) +
  annotation_custom(img_saint_1 %>% rasterGrob(), 
                    xmin=5.2, xmax=6.2, ymin=1.35, ymax=1.55) +
  coord_cartesian(clip = "off")


```

```{r map n table dataset}

wc_map <- inner_join(wc_all_s_points, wc_all_labeled_wide %>% group_by(wc_countries) %>% 
             filter(., n == max(n)) %>% select(., wc_countries, n), by = "wc_countries") %>% 
  inner_join(., wc_all_labeled_long %>% count(wc_countries), by = "wc_countries")

uk_agg <- wc_map %>% filter(., wc_countries %in% c("England", "Scotland", "Wales")) %>% bind_cols(., cont = rep("United Kingdom", 3))

uk_agg.1 <- aggregate(wc_map %>% filter(., wc_countries %in% c("England", "Scotland", "Wales")) %>% .[,2:4], 
          by = list(wc_countries = uk_agg$cont), FUN = sum)

uk_agg.2 <- uk_agg.1 %>% mutate(., n.x = 4, n.y = 7) # basically, england "carries football" in britain.

wc_map <- wc_map %>% bind_rows(., uk_agg.2)

 # Add stages

max_stage <- character(0) 
 
for (i in wc_map$n.x) {
   if (i == 1 ) {
   max_stage <- c(max_stage, "Group stage")
 } else if (i == 2) {
   max_stage <- c(max_stage, "Last 16")
 } else if (i == 3) {
   max_stage <- c(max_stage, "Quarter finals")
 } else if (i == 4) {
   max_stage <- c(max_stage, "Semi finals")
 } else if (i == 5) {
   max_stage <- c(max_stage, "Final")
 } else if (i == 6) {
   max_stage <- c(max_stage, "WC Winners")
 }
}

winners <- numeric(0) 
 
for (i in wc_map$wc_countries) {
   if (i == "Argentina" ) {
   winners <- c(winners, 1)
 } else if (i == "Brazil") {
   winners <- c(winners, 1)
 } else if (i == "France") {
   winners <- c(winners, 2)
 } else if (i == "Germany") {
   winners <- c(winners, 1)
 } else if (i == "Italy") {
   winners <- c(winners, 1)
 } else if (i == "Spain") {
   winners <- c(winners, 1)
 } else 
   winners <- c(winners, 0)
   }

wc_map <- bind_cols(wc_map, "max_stage" = max_stage, "wc_wins" = winners)

  # Detect rebels

# left_join(st_transform(ne_countries(scale = 'medium', type = 'countries', returnclass = 'sf') %>%
#                           select("name_long", "name", "continent")), wc_map, 
#            by = c("name" = "wc_countries")) %>% filter(continent == "North America") %>% View()
# 
# anti_join(wc_map, st_transform(ne_countries(scale = 'medium', type = 'countries', 
#                                             returnclass = 'sf')) %>% 
#   select("name_long", "name", "continent"), 
#   by = c("wc_countries" = "name")
#   )

  # Korea Republic (south korea) = Republic of Korea (long) ; Korea (name)
  # IR Iran = Iran (long) ; Iran (name)
  # Türkiye  = Turkey (long) ; Turkey (name)
  # China PR  = China (long) ; China (name)
  # Korea DPR  = 	Dem. Rep. Korea (long) ; 	Dem. Rep. Korea (name)
  # Rep. of Ireland  = 	Ireland (long) ; 	Ireland (name)
  # Bosnia & Herz'na  = 	Bosnia and Herzegovina (long) ; 	Bosnia and Herz. (name)
  # Czech Republic  = 		Czech Republic (long) ; Czech Rep. (name)
  # Trin & Tobago  = 	Trinidad and Tobago (long) ; Trinidad and Tobago (name)

  # replacing "rebels" manually...

rebels_list <- c("Korea Republic", "IR Iran", "Türkiye", "Rep. of Ireland", "Bosnia & Herz'na", "China PR", "Czech Republic", "Korea DPR",  "Trin & Tobago")

reb_corrected_list <- c("Korea", "Iran", "Turkey", "Ireland", "Bosnia and Herz.", "China", "Czech Rep.", "Dem. Rep. Korea", "Trinidad and Tobago")

wc_map[1] <- sapply(wc_map[1], function(o)
  replace(o, o %in% rebels_list, reb_corrected_list))

ISO_tab <- read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//ISO_tab.xlsx")

wc_map_wcs_i <- st_transform(ne_countries(scale = 'medium', type = 'countries', 
                                          returnclass = 'sf')) %>%
           select("name", "continent") %>%
  left_join(.,  wc_map, by = c("name" = "wc_countries")) %>% 
  left_join(., ISO_tab, by = c("name" = "countries"))

wc_map_wcs_i$sum_s_points <- replace_na(wc_map_wcs_i$sum_s_points, 0) 

text_map <- paste(wc_map_wcs_i$name, '\n',
  "WCS_I: ", wc_map_wcs_i$sum_s_points, '\n', 
  "WC Played (n): ", wc_map_wcs_i$n.y, '\n', 
  "Max. stage reached: ", wc_map_wcs_i$max_stage, '\n', 
  "WC Won (n): ", wc_map_wcs_i$wc_wins) %>%
  lapply(htmltools::HTML)

wc_map <-  wc_map %>% left_join(., wc_map_wcs_i %>% select(., name, continent), 
                      by = c("wc_countries" = "name")) %>% mutate(continent = replace_na(continent, "Europe")) # Only 'cause I know NAs came for europeans

# path_xlsx.s <- "C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success"
#  
# list_datasets <- list(wc_map, ISO_tab)
#  
# lapply(list_datasets, function(o){ 
#   write.xlsx(o, path_xlsx.s)  
#  })
# 
# read.xlsx("C://Users//santi//Desktop//saint_analytics//projects_&_work//saint_sports//wc_success//wc_map.xlsx")


```

### **WCS_I results: Map and Table**

```{r clorophert map n table, fig.height=5, fig.width=9, fig.align='center'}


p <- list(projection = list(type = 'natural earth'), 
          showcountries = TRUE, countrycolor = "black", 
          showland = TRUE, landcolor = "white")


plot_geo(wc_map_wcs_i, locationmode = 'code', locations = ~ISO_codes) %>% 
  add_trace(z = ~sum_s_points, text = text_map, hoverinfo = "text", 
            color = ~sum_s_points, colors = 'Blues', 
            marker = list(line = list(color = "green", width = .5))) %>% 
  add_annotations(text = paste("~ 5 countries where excluided from the map: England, Scotland, Serbia & Montenegro, Yugoslavia, and Wales.", "* British could not be set appart, and thus were aggregated as United Kingdom in the map.","* Serbia & Montenegro, and Yugoslavia don't exist anymore.", sep = "\n"), showarrow = F, x = .5, y = -0.1) %>%
  colorbar(title = "Index sum", x = 1, y = .8) %>% 
  layout(title = paste("<b>WCS_I around the globe<br>(1998 - 2022)</b>"), geo = p,
         images = list(list(source = raster2uri(pen), 
                             xref = "paper", yref = "paper", x= .85, y= 1.06, 
                             sizex = .17, sizey = .14)))


```



```{r clorophert table}

reactable(wc_map %>% select(., wc_countries, continent, sum_s_points) %>% 
            filter(., !wc_countries == "United Kingdom"), 
          pagination = F, height = 255, width = 480, filterable = TRUE,
          outlined = TRUE, striped = TRUE,
          columns = list(
            wc_countries = colDef(name = "Countries", width = 180),
            continent = colDef(name = "Continent", width = 180),
            sum_s_points = colDef(name = "WCS_I", width = 100, align = "center")), 
          theme = reactableTheme(searchInputStyle = list(width = "100%")))

```

## **Appendix**
  
```{r, include=FALSE}
succ_text <- c("Success in victory...?", "Success in defeat...?", "Loose, yet\ndominating the game?",
               "Win while\nbeing dominant?",
               "Win regardless of\nwho's dominant?",
               "Winning without\ndominance?", 
               "What is dominance...?", 
               "Take more chances\nthan the opponent?", 
               "Control the game's\nmain instrument (the ball)?", 
               "Impose tactics\nover the opponents'?") 


could_nt <- c("Could be", "Shouldn't be", "Shouldn't be", rep("Could be", 3), 
              rep("Dominance...?", 4))

coord_y_succ <- c(8.5, 8.5, rep(6.25,4), 3, rep(1,3))
coord_x_succ <- c(28, 6.5, 6.5, 19.5, 28, 36.5, 20, 7, 20, 33)


figi <- ggplot() +  
  geom_segment(data = data.frame(x = c(6.5, rep(28, 3), rep(20, 3)),
                                 xend = c(6.5, 20, 28, 36, 7, 20, 33),
                                 y = c(rep(8.5,4), rep(3, 3)), 
                                  yend = c(rep(6.5, 4), rep(1.5, 3))), 
                aes(x = x, xend = xend, y = y, yend = yend), 
            color = "black", alpha = .7,
            linejoin = c('round'), linewidth = 1.5,
            arrow = NULL) +  
  geom_segment(data = data.frame(x = c(0.1, 41, rep(0.1,3)),
                                 xend = c(0.1, 41, rep(41,3)),
                                 y = c(rep(0.1, 2),0.1, 10, 4), 
                                  yend = c(rep(10, 2), 0.1, 10, 4)), 
                aes(x = x, xend = xend, y = y, yend = yend), 
            color = "black", 
            linejoin = c('round'),
            arrow = NULL) +  
  geom_label(data = data.frame(coord_x_succ, coord_y_succ, succ_text, could_nt), 
             aes(x = coord_x_succ, y = coord_y_succ, label = succ_text, 
                 fill = could_nt), size = 3.2) + 
  geom_point(aes(x = 14, y = 4), size = 4, color = "black", alpha = .8) +
  geom_segment(aes(x = 14, y = 10, xend = 14, yend = 4), 
               color = "black", linetype = "dashed") + 
  ylim(0,10) + xlim(0,41.5) + 
  labs(title = "'What is success in football?'",
       subtitle = "Understanding the complexity of the question in hand", 
       caption = paste("A great question takes to another great question, to define\n success, one has to deinfe dominance")) + theme_void() +
  theme(plot.title.position = "plot", plot.title = element_text(hjust = 0),
        plot.subtitle = element_text(hjust = 0), 
        plot.margin = margin(0, 0, 0, .3, "cm"), 
        plot.caption = element_text(hjust = 0),
        plot.caption.position = "panel", 
        axis.text = element_blank(), axis.ticks = element_blank(), 
        axis.title = element_blank(), legend.position = "none") +
  annotation_custom(img_saint_1 %>% rasterGrob(), 
                    xmin=32, xmax=41, ymin=9.2, ymax=13.4) +
  coord_cartesian(clip = "off")
  
```

### **Success...?**


```{r pressure, echo=FALSE, fig.width=6, fig.height=4.2}
figi
```


### **2nd Map (with higher resolution)**
  
```{r clorophert map II, fig.height=5, fig.width=9, fig.align='center'}
g <- list(projection = list(type = 'natural earth'), 
           showcountries = TRUE, countrycolor = "black", 
          showland = TRUE, landcolor = "white" , resolution = 50)

plot_geo(wc_map_wcs_i, locationmode = 'code', locations = ~ISO_codes) %>% 
  add_trace(z = ~sum_s_points, text = text_map, hoverinfo = "text", 
            color = ~sum_s_points, colors = 'Greens', 
            marker = list(line = list(color = "green", width = .5))) %>% 
  add_annotations(text = paste("~ 5 countries where excluided from the map: England, Scotland, Serbia & Montenegro, Yugoslavia, and Wales.", "* British could not be set appart, and thus were aggregated as United Kingdom in the map.","* Serbia & Montenegro, and Yugoslavia don't exist anymore.", sep = "\n"), showarrow = F, x = .5, y = -0.1) %>%
  colorbar(title = "Index sum", x = 1, y = .8) %>% 
  layout(title = paste("<b>WCS_I around the globe<br>(1998 - 2022)</b>"), geo = g,
         images = list(list(source = raster2uri(pen), 
                             xref = "paper", yref = "paper", x= .85, y= 1.06, 
                             sizex = .17, sizey = .14)))


```

### **data sets**

  * **Map dataset**

```{r table I}

wc_map_wcs_i %>% select(., -c(n.x, n.y)) %>% datatable(rownames = F, 
                              extensions = 'Buttons',
                              options = list(dom = 'Blfrtip',
                                             buttons = c('copy', 'csv', 'excel'), 
                           pageLength = 4, lengthMenu = c(1, 2, 4)))



```

  * **Summary dataset**
  
```{r table II}

wc_map %>% select(., -c(n.x, n.y)) %>% datatable(rownames = F, 
                              extensions = 'Buttons',
                              options = list(dom = 'Blfrtip',
                                             buttons = c('copy', 'csv', 'excel'), 
                           pageLength = 4, lengthMenu = c(4, 8, 12)))



```
  
  * **Long dataset**
  
```{r table III}

wc_all_labeled_long %>% select(., -n) %>% datatable(rownames = F, 
                              extensions = 'Buttons',
                              options = list(dom = 'Blfrtip',
                                             buttons = c('copy', 'csv', 'excel'), 
                           pageLength = 4, lengthMenu = c(4, 8, 12)))



```
  
  * **Wide dataset**

```{r table IV}

wc_all_labeled_wide_sum %>% select(., -n) %>% datatable(rownames = F, 
                              extensions = 'Buttons',
                              options = list(dom = 'Blfrtip',
                                             buttons = c('copy', 'csv', 'excel'), 
                           pageLength = 4, lengthMenu = c(4, 8, 12)))



```

### **imagery credits**

```{r table V}



reactable(img_cred, pagination = FALSE, highlight = TRUE, 
          height = 175,
          columns = list(
    imagery_tag = colDef(name = "Image label"),
    imagery_credit = colDef(name = "Credits (w/link)", 
                            html = TRUE, 
                            cell = function(value, index) {
      sprintf('<a href="%s" target="_blank">%s</a>', img_cred$imagery_link[index], value)
    }), 
    imagery_link = colDef(show = F) 
  )
)



```
